{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Physics Paragraph

	\paragraph{Input from Physics Analysis}
	\vspace{-0.2cm}

>>>>

	\paragraph{Input from Physics Analysis}
	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates. For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value. This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise. Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
	\vspace{-0.2cm}
